Type cones of $\b{g}$-vector fans

### 2019-02-15 thirdPaper/draft/typeConeAssociahedra.tex
notation

\begin{theorem}\label{theorem::extricats}
Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits an extriangle~$T_1^X\infl T_0^X\defl X\dashrightarrow$ with~$T_0^X, T_1^X\in\add(T)$, and for any~$T'\in\add(T)$ the morphism~$T'\to 0$ is an inflation. Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
\[
 L:=\left\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \right\}
\]
generates the kernel of the canonical projection~$\b g:\Ksp(\cat) \to \kzero{\cat}$. 
In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{theorem}

>>>>

\begin{theorem}\label{theorem::extricats}
Assume that~$\cat$ is a~$\field$-linear, Ext-finite, Krull--Schmidt, extriangulated category with Auslander--Reiten--Serre duality.
Assume that~$T$ is a projective object of~$\cat$ such that any~$X\in\cat$ admits an extriangle~$T_1^X\infl T_0^X\defl X\dashrightarrow$ with~$T_0^X, T_1^X\in\add(T)$, and the morphism~$T\to 0$ is an inflation. Fix a conflation~$T\to 0 \to \susp T$. Then~$\cat$ has only finitely many isomorphism classes of indecomposable objects if and only if the set
\[
 L:=\left\{\ell_X \ | \ X\in \ind(\cat)\setminus \add(\susp T) \right\}
\]
generates the kernel of the canonical projection~$\b g:\Ksp(\cat) \to \kzero{\cat}$. 
In this case, the set~$L$ is a basis of the kernel of~$\b g$, and for any $x\in \ker(\b g)$, we have that
 \[
  x= \sum_{A\in \ind(\cat) \setminus \add(\susp T)} \frac{\langle x, A \rangle}{\langle \ell_A, A \rangle} \ell_A.
 \]
\end{theorem}
